### 2020-07-18 article.tex
Add sentence and project reference

\section*{Acknowledgments}
The authors would like to thank S. Balay, J. Brown, V. Hapla, M. Knepley,
and B. Smith for reviewing the successive merge requests in the PETSc
repository. This work was granted access to the GENCI-sponsored HPC resources of:
\begin{itemize}
    \item TGCC@CEA under allocation A0070607519;
    \item IDRIS@CNRS under allocation AP010611780.
\end{itemize}
% We would like to acknowledge the assistance of volunteers in putting
% together this example manuscript and supplement.

>>>>

Concerning SLEPc, as a future work we plan to implement new solvers (or extend existing
ones) to further exploit the block solve primitives, for instance block Krylov-Schur.

\section*{Acknowledgments}
The authors would like to thank S. Balay, J. Brown, V. Hapla, M. Knepley,
and B. Smith for reviewing the successive merge requests in the PETSc
repository. This work was granted access to the GENCI-sponsored HPC resources of:
\begin{itemize}
    \item TGCC@CEA under allocation A0070607519;
    \item IDRIS@CNRS under allocation AP010611780.
\end{itemize}
Jose E.~Roman was supported by the Spanish Agencia Estatal de Investigaci\'{o}n (AEI) under project SLEPc-DA (PID2019-107379RB-I00).
% We would like to acknowledge the assistance of volunteers in putting
% together this example manuscript and supplement.
